From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-09 papers/ACL2020/acl2020_main.tex
[ACL2020] note in main on what to add
changes in abstract

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose.  
Based on large-scale, thouroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that object classification models ``spontaneously'' learn good entry-level names and that they can be further finetuned via transfer learning. 
\sz{A short sentence on human-like errors?}
\end{abstract}

@@

\section{ManyNames: A Source for Entry-Level Names}
\label{sec:manynames}
\cs{to add: footnote saying that the \mn data will be published upon acceptance of the paper.}
\input{manynames}

>>>>

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by a single annotator. 
Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
on predicting entry-level than \arbitrary names, despite being trained on  \arbitrary names.
We further fine-tune these models via transfer learning and systematically vary their training vocabulary.
\sz{something ...}
\end{abstract}

@@

\section{ManyNames: A Source for Entry-Level Names}
\label{sec:manynames}
%\cs{to add: footnote saying that the \mn data will be published upon acceptance of the paper.}
\input{manynames}
